---
title: "Week 1 Weekend Homework"
output: html_notebook
---

```{r}
library(tidyverse)
library(ggplot2)
library(lubridate)



## Dataset -----
goodreads <- read.csv("books.csv")

 glimpse(goodreads)
# distinct(goodreads)
# names(goodreads)

```

```{r}
goodreads_books <- goodreads %>% 
  select(title, authors, average_rating, 
         language_code, ratings_count, publisher, num_pages) %>% 
  filter(ratings_count > 100000) 
```

```{r}
goodreads_books %>% 
    summarise(count = sum(is.na(average_rating))) %>% 
  pull()

goodreads_books %>% 
summarise(count = sum(is.na(ratings_count))) %>% 
  pull()
```
## Highest rated titles

```{r}
goodreads_books %>% 
  arrange(average_rating) %>% 
  tail(5)
```

For this metric I only included books that had more than 100,000 reviews. 

## Author with the highest average rating 

```{r}
goodreads_books %>% 
  group_by(authors) %>% 
  summarise(average_rating = mean(average_rating)) %>% 
  arrange(desc(average_rating)) %>% 
  head(5)

```

#Author with the most reviews 

```{r}
goodreads_books %>% 
  group_by(authors) %>% 
  summarise(total_reviews = sum(ratings_count)) %>% 
  arrange(desc(total_reviews)) %>% 
  head(5)
```
From this we can see the most popular author is J.K Rowling


# Does book lenght affect rating? 
```{r}
length_v_rating <- goodreads_books %>% 
  head(50) %>% 
  ggplot(aes(x = num_pages, y = average_rating)) + geom_point() + geom_smooth(method = "lm", se = FALSE)

length_v_rating
  
  
  
```

From this graph we can see that the longer a book is the more likely it is to be rated higher.  

#How puplication year affects rating count

```{r}
book_rating_date <- goodreads %>% 
  select(title, ratings_count, publication_date) 
```

```{r}
date_published <- book_rating_date %>%
  as.Date(publication_date, format = "%m%d&y") #%>% 
  #year <- format(date_published, "%Y")
  

```
Need to ask for help to reformat "publication_date" into a date so I can then extract the year
```

