---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(CodeClanData)
```

```{r}
drinks_content
```

## Question 1

```{r}
  dim(drinks_content)
```
242 Observations, 18 Variables 

```{r}
glimpse(drinks_content)
```
variable names + types

##Question 2
```{r}
selected_drinks <-  drinks_content %>% 
select(Beverage_category, Beverage, Beverage_prep, Calories)

sum(is.na(selected_drinks))
```

##Question 3 
```{r}
drinks_content %>% 
  mutate(calorie_diff = Calories - 135, .after = Calories)
```

## Question 4 
```{r}
drinks_content %>% 
  select(Beverage_category, Calories) %>% 
  group_by(Beverage_category) %>% 
  summarise(mean_calories = mean(Calories)) %>% 
  arrange(desc(mean_calories))
  


  
```
The categories with the highest mean calories are: `Smoothies`, `Frappuccino® Blended Coffee` & `Signature Espresso Drinks`
The Categories with the least are: `Classic Espresso Drinks`, `Shaken Iced Beverages`& `Shaken Iced Beverages` 

##Question 5 
```{r}
drinks_content %>% 
  select(Beverage_prep, Calories) %>% 
  group_by(Beverage_prep) %>% 
  summarise(mean_calories = mean(Calories)) %>% 
  arrange(desc(mean_calories))

```

## Question 6 
First work out average Calories
```{r}
drinks_content %>% 
  summarise(mean(Calories))
```
Then 
```{r}
drinks_content %>% 
  select(Beverage_prep, Calories) %>% 
  group_by(Beverage_prep) %>% 
  summarise(mean_calories = mean(Calories)) %>% 
  arrange(desc(mean_calories)) %>% 
  filter(mean_calories > 193.8719)
```



## Question 7 
```{r}
drinks_content %>% 
  select(Beverage, Beverage_category, Beverage_prep, Calories) %>% 
 arrange(Calories) 
```

Short Brewed Coffee