---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(factoextra)
library(GGally)
library(broom)

mall_customers <- read_csv("~/Desktop/CodeClan/codeclan_homework_mark/week_11/day_03/data/mall_customers.csv")%>% 
  clean_names() %>% 
  select(-customer_id, -gender)
```

# Task 1
```{r}
mall_customers %>% 
ggpairs()
```
From this I can't see any really promising correlations, potentially age? 


# Task 2
```{r}
mall_scale <- mall_customers %>% 
  mutate(across(age:annual_income_k,
         .fns = scale))
```

```{r}
clustered_mall <- mall_scale %>% 
  kmeans(centers = 6,
         nstart = 25)

clustered_mall
```

```{r}
clustered_mall%>% 
  tidy(col.names = colnames(mall_scale))
```

```{r}
min_k <- 1
max_k <- 20

mall_k_clusters <- tibble(k = min_k:max_k) %>% 
  mutate(kclust = map(k, ~kmeans(mall_scale, center = .x, nstart = 25)),
         tidied = map(kclust, tidy),
         glanced = map(kclust, glance),
         augmented = map(kclust, augment, mall_customers))

mall_k_clusters
```

```{r}
clusterings <- mall_k_clusters %>% 
  unnest(glanced)

clusterings
```

```{r}
clusterings %>% 
  ggplot(aes(x = k, 
             y = tot.withinss)) +
  geom_point() + 
   geom_line() +
   scale_x_continuous( breaks = seq(1, 20, 1))
```

```{r}
fviz_nbclust(mall_scale,
             kmeans,
             method = "silhouette",
             nstart = 25)
```
 Using the elbow method k = 3 seems to be the best fit

# Task 3

```{r}
clusterings %>% 
  unnest(augmented) %>% 
  filter(k == 3) %>% 
  ggplot(aes(x = age, 
             y = annual_income_k,
             colour = .cluster)) +
  geom_point() +
  labs(title = "Age vs Annual Income",
       x = "Age",
       y = "Annual Income")
  
```
From this graph I found it hard ro see any distinct groupings, I don't think the
data is very suited to clustering

```{r}
clusterings %>% 
  unnest(augmented) %>% 
  filter(k == 3) %>% 
  ggplot(aes(x = age, 
             y = spending_score_1_100,
             colour = .cluster)) +
  geom_point() +
  labs(title = "Age vs Spending Score",
       x = "Age",
       y = "Spending Score")
  
```
Here we can see 3 distinct Cluster for spending scores.

Cluster 1: Bargain Hunters
Cluster 2: Name TBC
Cluster 3: Shop till you drop

I think the data is good for clustering. 

Perhapbs you could have 3 campaigns: 
- One for some sort of budget sale aimed at cluster 1
- Cluster 2, also some sort of sale but perhapbs on slightly more expensive products
- Cluster 3 market the best new products


```{r}
clusterings %>% 
  unnest(augmented) %>% 
  filter(k == 3) %>% 
  ggplot(aes(x = annual_income_k, 
             y = spending_score_1_100,
             colour = .cluster)) +
  geom_point() +
  labs(title = "Annual Income vs Spending Score",
       x = "Annual Income",
       y = "Spending Score")
```
I also feel this data is good for clustering but I'm actually not sure what it 
tells you because there is a fairly even spread of the data, in realation to income. 
