---
title: "R Notebook"
output: html_notebook
---

## Bootstrapping and confidence intervals

### Learning Objectives 

- Understand the concepts


```{r}
summary_popn
summary_sample_200
```

_confidence interval_

(__not right__) 
the range of values whitin which there is a 95% chance that the true population value lies. 

Strictly, we can't really say that

95% CI: really it's about the _confidence_ we have in our _CI_, as opposed to the confidence we 
would like to have in our estimate

```{r}
32.33624 + c(-1.770078, 170078)
```


Think of this as like fishing with either a spear or a net.

The 'spear' is the point estimate,

while rhe 'net' is the confidence interval. 

We generally talk in terms of a 95% CI or 99% CI

To be more certain of catching a fish, you have to make your net bigger. 
To have more confidence in the point estimate, you have to make the confidence interavl wider. 

### Bootstrapping 

Re-sampling __with__ replacement 

Why would we ever replace our samples? 

```{r}
telco_200 <- read_csv("4_confidence_intervals/data/telecomms_churn_200_sample.csv") %>% 
  clean_names()

glimpse(telco_200)
```

```{r}
bootstrap_resample_200 <- sample_200 %>%
  rep_sample_n(size = 200, replace = TRUE, reps = 5000) %>%
  summarise(
    mean_tenure = mean(tenure)
  )

bootstrap_resample_200
```

Task - 5 mins
How close is the bootstrapped sampling distribution of mean(tenure) to the one shown above?
Plot a histogram of the bootstrapped sampling distribution
Calculate the standard error in mean(tenure) and compare it with the previous value 1.72 months [remember: this is just the sd() of the sampling distribution]

```{r}
bootstrap_resample_200 %>% 
  ggplot(aes(x = mean_tenure)) +
  geom_histogram(bins = 25, colour = "white", fill = "blue")
```

```{r}
std_error <- bootstrap_resample_200 %>% 
  summarise(
    se_mean_tenure = sd(mean_tenure)
    )
```
1. We resample with replacement, samples of the same size of our orginal sample
  - we replace because if we didn't all reps would be identical 
      - if we resample beyond the size of our sample...
        -consider sampling 400
  - If we resample with smaller sizes we're giving up some possible information 
  - Rare values are rare, common values are common
      - with replacement, we are placing heavier weight on the common values

## CI from bs

```{r}
bootstrap_resample_200 %>% 
  ggplot(aes(x = mean_tenure)) +
  geom_histogram(bins = 25, colour = "white", fill = "blue")
```

A confidence interval is an interval 
that means it is composed of two limits 

we want a 95%CI
(0.025 = 2.5%)
```{r}
bootstrap_resample_200 %>% 
  summarise(
    mean = mean(mean_tenure),
    lower_bound = quantile(mean_tenure, prob = 0.025),
    upper_bound = quantile(mean_tenure, prob = 0.975)
  )
```

### Working using the `infer` package

1. `specify()` which variable we are interested in (`tenure`) 
2. `generate()` our replicate resamples
3. `calculate()` the summary stats we are interested in

How many obs do we have for each replicate?
It's 200 
BECAUSE we are bootstrapping 
```{r}
infer_resample <- telco_200 %>% 
  specify(response = tenure) %>% 
  generate(reps = 5000, type = 'bootstrap') %>% 
  calculate(stat = "mean")
```
### Calculate our CI

we want to get the standard error of our sample means 

```{r}
infer_ci_95 <- infer_resample %>% 
  get_confidence_interval(level = 0.95, type = "percentile") 
```

```{r}
infer_resample %>% 
  visualise(bins = 25) +
  shade_confidence_interval(endpoints = infer_ci_95)
```

```{r}
infer_resample %>% 
  summarise(mean = mean(stat)) 
```

