---
title: "Distributions homework"
output: html_notebook
---
```{r}
library(tidyverse)
library(janitor)
```

# Question 1: Load the data, clean_names() and explore it.
```{r}
items <- read_csv("data/20190928-items.csv") %>% 
  clean_names() 
```

```{r}
glimpse(items)
```

# Question 2: Find the brand with the highest numbers of phones in the dataset.
```{r}
items %>% 
  count(brand) %>% 
  arrange(desc(n))
```
Samsung has the highest number of phones in the dataset

# Question 3: For your top brand, plot the distribution of phone ratings as a 
probability density, overlaying a fitted normal distribution.
Do you think the normal distribution provides a good model of these ratings?

```{r}
samsung_stats <- items %>% 
  filter(brand == "Samsung") %>%
  summarise(num = n(),
            mean =mean(rating),
            sd = sd(rating))

samsung_stats
```


```{r}
items %>% 
    filter(brand == "Samsung") %>%
  ggplot(aes(x = rating)) + 
  geom_histogram(aes(y = after_stat(density)),  colour = "white", bins = 25) +
  stat_function(
    fun = dnorm, 
    args = list(
      mean = samsung_stats$mean,
      sd = samsung_stats$sd
    ),
    col = "red"
  )
  
```

I think the shape of the bell curve on the normal distribution line does encompass the shape of the data so in that sense it does a good job of capturing where most of the ratings are. It does however tail off quite a bit on the left as opposed to the right but I don't think that pulls the curve away from the mean.

# Question 4: We can be more quantitative in comparing the distribution of top brand ratings with a normal distribution. You calculated the mean() and sd() of your distribution in an earlier question. Use these values to calculate the proportions of ratings within one-, two- and three standard deviations of the mean. Compare these proportions with those you expect for a normal distribution.
```{r}
samsung_ratings <- items %>% 
  select(brand, rating) %>% 
  filter(brand == "Samsung")
```


```{r}
samsung_ratings %>%
  filter(rating >= samsung_stats$mean - samsung_stats$sd) %>%
  filter(rating <= samsung_stats$mean + samsung_stats$sd) %>%
  summarise(prop_within_1sd = n() / nrow(samsung_ratings))
```
```{r}
samsung_ratings %>%
  filter(rating >= samsung_stats$mean - 2 * samsung_stats$sd) %>%
  filter(rating <= samsung_stats$mean + 2 * samsung_stats$sd) %>%
  summarise(prop_within_2sd = n() / nrow(samsung_ratings))
```

```{r}
samsung_ratings %>%
  filter(rating >= samsung_stats$mean - 3 * samsung_stats$sd) %>%
  filter(rating <= samsung_stats$mean + 3 * samsung_stats$sd) %>%
  summarise(prop_within_3sd = n() / nrow(samsung_ratings))
```

