---
title: "R Notebook"
output: html_notebook
---

Question 1: Load in the libraries you need, and look at the backpack data. Take note of variable names and dimensions

```{r}
library(ggplot2)
library(tidyverse)
```


```{r}
backpack <- CodeClanData::backpack

glimpse(backpack)
names(backpack)
```

Question 2: What is the distribution of backpack weights that students are carrying?
```{r}
ggplot(backpack) +
  aes(x = backpack_weight) + 
   geom_histogram(binwidth = 5) +
  theme_minimal()
```

Question 3: Are there differences in backpack weight between sex?
```{r}
ggplot(backpack, aes(x = year, y = backpack_weight, fill = sex)) +
  geom_col() +
  labs(title = "Backpack weight by sex",
       x = "Year",
       y = "Backpack Weight") +
  theme_minimal()
```
Question 4: What is the relationship between body weight and backpack weight?
```{r}
ggplot(backpack, aes(x = body_weight, y = backpack_weight)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Body Weight",
       y = "Backpack Weight") +
  theme_minimal()

```
From this graph we can see that someone with a greater bodyweight is more likely to have a heavier bag. However there are a few outliers 

Question 5: Is this relationship different between men and women? Choose an appropriate plot and interpret your findings.
```{r}
ggplot(backpack, aes(x = body_weight, y = backpack_weight, colour = sex)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Body Weight",
       y = "Backpack Weight") +
  facet_wrap(~sex) +
  theme_minimal()
```
Here we can see that the trend line is greater for womnen so they are more likely to have a heavier bag with increased bodyweight when compared to men. 
However both trendlines suggest that backpack wight will increase with bodyweight.

Question 6: 
```{r}
prop_back_problems <- mean(backpack$back_problems)


ggplot(data.frame(BackProblems = c("Yes", "No"), Proportion = c(prop_back_problems, 1 - prop_back_problems)),
       aes(x = "", y = Proportion, fill = BackProblems)) +
  geom_bar(stat = "identity", width = 1, color = "white") +
  coord_polar("y", start = 0) +
  theme_void() +
  ggtitle("Proportion of students with back problems")
```
From this graph we can see the majority off the students do not have back problems

Question 7: Is this proportion different between men and women?
```{r}

prop_back_problems <- backpack %>%
  group_by(sex) %>%
  summarise(prop_back_problems = mean(back_problems))


ggplot(prop_back_problems, aes(x = sex, y = prop_back_problems, fill = sex)) +
  geom_col() +
  ylab("Proportion reporting back problems") +
  ggtitle("Back problems by sex") +
  theme_minimal()
```
Here we can see that backprolems are more common with female students

Question 8:Now you’ve investigated your data separately, create plots to describe the relationship between backpack weight, body weight, gender and reported backpain.
```{r}

ggplot(backpack, aes(x = body_weight, y = backpack_weight, color = back_problems)) +
  geom_point() +
  facet_wrap(~ sex) +
  labs(x = "Body Weight", y = "Backpack Weight", color = "Back Pain") +
  ggtitle("Backpack Weight vs. Body Weight by Gender")
```
```{r}

ggplot(backpack, aes(x = ratio, y = backpack_weight, color = back_problems)) +
  geom_point() +
  facet_wrap(~ sex) +
  labs(x = "Ratio (Backpack Weight / Body Weight)", y = "Backpack Weight", color = "Back Pain") +
  ggtitle("Backpack Weight vs. Ratio by Gender")
```

