---
title: "R Notebook"
output: html_notebook
---
```{r}
library(ggplot2)
```

```{r}
col_scheme <- c("#E89FE9", "#50434F", "#B6A7B5", "#F9A472", "#BD7040")

qb_revenue_breakdown <- CodeClanData::qb_revenue_breakdown

qb_monthly_sales <- CodeClanData::qb_monthly_sales

qb_competitors <- CodeClanData::qb_competitors

qb_device_data <- CodeClanData::qb_device_data
```

Question 1: Take the data in the dataset qb_revenue_breakdown and make a stacked bar chart showing the sources of revenue across the two years in the dataset. 
```{r}
qb_revenue_breakdown %>% 
  ggplot(aes(x = Year, y = Revenue, fill = Product)) +
  geom_bar(stat = "identity") +
  labs(
    x = "Year",
    y = "Revenue (£)",
    title = "Product Revenue Breakdown 2018 vs 2019") +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10),
    legend.title = element_blank(),
    legend.text = element_text(size = 10),
    legend.key = element_rect(fill = col_scheme, colour = "white"),
    legend.key.size = unit(12, "pt"),
  ) +
  scale_fill_manual(values = col_scheme)
```

Question 2: Make a line chart showing monthly sales of the “flagship product” - the ‘KwikBit Unit 1’ - over the last year.  
```{r}
Kwikibit_2019_Sales <- qb_monthly_sales %>% 
  filter(Cashflow == "Kwikbit Unit 1 Sales",
          year(Date) == 2019 )
```


```{r}
Kwikibit_2019_Sales %>% 
ggplot(aes(x = Date, y = Amount, colour = Cashflow)) +
  geom_line(size = 1, colour = col_scheme[1]) +
  geom_point(size = 3, colour = col_scheme[2]) +
  labs(
       x = "Month", 
       y = "Sales Total (£)",
       title = "Monthly Sales of KwikBit Unit 1 - 2019") +
  scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  scale_colour_manual(values = col_scheme[1]) +
  theme_bw() +
  theme(
        text = element_text(size = 12),
        plot.title = element_text(size = 14, hjust = 0.5),
        axis.title = element_text(size = 12),
        legend.position = "none"
       )
```


Question 3: Make a line chart showing monthly revenue and costs over the last year.

```{r}
costs_and_revenue_2019 <- qb_monthly_sales %>% 
  filter(Cashflow %in% c("Total Revenue","Cost"), 
          year(Date) == 2019 
           )

costs_and_revenue_2019
```

```{r}
costs_and_revenue_2019 %>% 
ggplot(aes(x = Date, y = Amount, color = Cashflow)) +
  geom_line() +
  scale_x_date(date_labels = "%b %Y", date_breaks = "1 month")  +
  labs(
       x = "Month",
       y = "Amount (£)",
       title = "2019 Monthly Revenue Vs Costs",
       color = "Cashflow") +
  theme_minimal() +
  theme(
        axis.text = element_text(size = 10),
        axis.title = element_text(size = 12, face = "bold"),
        legend.position = "bottom",
        legend.title = element_blank(),
        legend.text = element_text(size = 10),
        legend.key.size = unit(0.5, "cm")) +
  scale_colour_manual(values = col_scheme)
```


Question 4: Show annual sales of personal fitness trackers over the last 5 years broken down by company as a ribbon plot
```{r}
qb_competitors %>% 
ggplot(aes(x = Year, y = Revenue, fill = Company)) + 
  geom_area(position='stack', alpha=0.7) +
  labs( 
       x = "Year", 
       y = "Revenue (£)",
       title = "Annual Sales of Competitor Personal Fitness Trackers") +
  scale_y_continuous(labels = scales::comma) +
  scale_fill_manual(values=col_scheme)
```

Question 5:
```{r}
qb_competitors %>% 
ggplot(aes(x = Year, y = Revenue, colour = Company)) +
  geom_line() +
  geom_point() +
  scale_colour_manual(values = col_scheme) +
  labs(title = "Annual Sales of Competitor Personal Fitness Trackers",
       x = "Year",
       y = "Revenue (£)") +
  scale_y_continuous(labels = scales::comma) +
  theme_bw() +
  theme(
        plot.title = element_text(size = 14, face = "bold"),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10))
```

Question 6: Now the company wants to compare the number of steps that their device counts vs. their competitors. Make a line graph of the number of steps throughout time, and use faceting to compare between companies and people


```{r}
qb_device_data_hourly <- qb_device_data %>% 
  group_by(device, hours) %>%
  summarise(step_count = sum(counts), .groups = "drop")

qb_device_data_hourly
```

```{r}
qb_device_data_hourly %>% 
ggplot(aes(x = hours, y = step_count, colour = device)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  facet_wrap(~ device) +
  labs(
       x = "Hours",
       y = "Total Steps",
       title = "Number Of Steps Counted Per Hour By Device ") +
  scale_colour_manual(values = col_scheme) +
  theme_bw() +
  theme(plot.title = element_text(size = 16, face = "bold"),
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        legend.position = "bottom",
        legend.text = element_text(size = 12))
```



