---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(gtools)
```

```{r}
titanic <- read_csv("data/titanic.csv")
```
# 1.1 The Titanic
```{r}
glimpse(titanic)
```
```{r}
titanic_surviors <- titanic%>% 
  mutate(crew = ifelse(class %in% c("engineering crew", "victualling crew" ,"restaurant staff", "deck crew"),TRUE, FALSE)) %>% 
  select(survived, crew)
```

#Probability of Crew Survival
```{r}
titanic_surviors %>% 
  filter(crew == TRUE) %>% 
  summarise(prob = sum(survived == "yes")/ n())
```

#Probability of Passenger Survival
```{r}
titanic_surviors %>% 
  filter(crew == FALSE) %>% 
  summarise(prob = sum(survived == "yes")/ n())
```
From these results we can see that statically speaking that passengers had a higher probability of surviving

## 1.2 Probability Consolidation Questions

#Question 1: If I roll a six-sided dice once, what is the probability of getting a number less than 5?
```{r}
4/6
```

# Question 2: How many outcomes are there in the sample space of an experiment in which we toss three dice?
```{r}
s_three_dice <- rolldie(3, nsides = 6)

s_three_dice
```
There are a possible 216 outcomes

Question 3: n an experiment where we roll four dice

```{r}
s_four_dice <- rolldie(4, nsides = 6) %>% 
  mutate(total = X1 + X2 + X3 + X4) %>% 
  filter(total == 5 | total == 6 | total == 7)
  

s_four_dice 
```
i) there are 34 outcomes where the total mof the four dice is equal to 5, 6 or 7

```{r}
34/1296
```
 ii) the probability of this is 0.02623457
 
 iii) The assumptions made are that: 
 -fair 6 sided dice are used. 
 -all dice are thrown at the same time

## Question 4: Five chairs are placed in a row in a room, along with five people of differing height. The people sit down randomly on the chairs. What is the probability that they sit in order of decreasing height, left to right?

```{r}
height_cm <- c(177, 180, 157, 164, 186)

length(height_cm)

seating_arrangements <-  as_tibble(
  permutations(n = length(height_cm),
               r = 5,
               v = height_cm,
               repeats.allowed = FALSE)
)

seating_arrangements
```

there are 120 possible outcomes for seating arrangement but only 1 where they sit from tallest to smallest. therefore the probability of this is 1/120 or 0.008333333

```{r}
1/120
```

